Nested sampling with multiple scalars

### 2015-09-15 Paper/ms.tex
Spaces and acknowledgements

% Keywords: add 3 to 10 keywords
\keyword{keyword; keyword; keyword}

@@

\section{Introduction}
Nested Sampling \citep{skilling} is an effective and popular
Monte Carlo algorithm for Bayesian computation and
statistical mechanics
\citep{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
In a Bayesian inference problem with unknown parameters denoted collectively
by a vector $\xx$, the
posterior distribution for the parameters given data $\data$ (and prior
information $I$) is:
\begin{eqnarray}
p(\xx | \data, I) &=&
\frac{p(\xx | I)p(\data | \xx, I)}{p(\data | I)}\\
&=& \frac{\pi(\xx)L(\xx)}{Z}
\end{eqnarray}
where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
function, and $Z$ is the normalising constant, known as the
``marginal likelihood'' or the ``evidence'':
\begin{eqnarray}
Z &=& \int \pi(\xx) L(\xx) \, \dx.
\end{eqnarray}

@@

\section{Properties of Nested sampling}
We seek an algorithm for computing the partition function
$Z(\alpha_1, \alpha_2)$ for a range of values of the $\alpha$s, from a single
run. To be considered a variant of Nested Sampling, we require that the method
satisfies the following requirements:
\begin{itemize}
\item The algorithm should begin with $n$ points drawn from the prior $\pi(\xx)$.
\item The algorithm should seek to explore regions where the values of
$S_1(\xx)$ and $S_2(\xx)$ are greater than what would be expected from the
prior.
\item The algorithm should try to move through a sequence of probability
distributions whose enclosed prior masses are approximately known.
\item The algorithm should be invariant to monotonic transformations of
$S_1$ and $S_2$, i.e. it should only depend on rankings of $S_1$ and $S_2$
values and not the values themselves.
\end{itemize}

@@

\section{Example: Potts model with some embellishments}
TBD

\section{A Diffusive Variant}
Have one walker, or a few (not a large number).

@@

>>>>

% Keywords: add 3 to 10 keywords
\keyword{nested sampling; bayesian computation; statistical mechanics}

@@

\section{Introduction}

Nested Sampling \citep{skilling} is an effective and popular
Monte Carlo algorithm for Bayesian computation and
statistical mechanics
\citep{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
In a Bayesian inference problem with unknown parameters denoted collectively
by a vector $\xx$, the
posterior distribution for the parameters given data $\data$ (and prior
information $I$) is:
\begin{eqnarray}
p(\xx | \data, I) &=&
\frac{p(\xx | I)p(\data | \xx, I)}{p(\data | I)}\\
&=& \frac{\pi(\xx)L(\xx)}{Z}
\end{eqnarray}
where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
function, and $Z$ is the normalising constant, known as the
``marginal likelihood'' or the ``evidence'':
\begin{eqnarray}
Z &=& \int \pi(\xx) L(\xx) \, \dx.
\end{eqnarray}

@@

\section{Properties of Nested sampling}

We seek an algorithm for computing the partition function
$Z(\alpha_1, \alpha_2)$ for a range of values of the $\alpha$s, from a single
run. To be considered a variant of Nested Sampling, we require that the method
satisfies the following requirements:
\begin{itemize}
\item The algorithm should begin with $n$ points drawn from the prior $\pi(\xx)$.
\item The algorithm should seek to explore regions where the values of
$S_1(\xx)$ and $S_2(\xx)$ are greater than what would be expected from the
prior.
\item The algorithm should try to move through a sequence of probability
distributions whose enclosed prior masses are approximately known.
\item The algorithm should be invariant to monotonic transformations of
$S_1$ and $S_2$, i.e. it should only depend on rankings of $S_1$ and $S_2$
values and not the values themselves.
\end{itemize}

@@

\section{Example: Potts model with some embellishments}

TBD

\section{A Diffusive Variant}

Have one walker, or a few (not a large number).

@@

\acknowledgments{Acknowledgements}

It is a pleasure to thank Gábor Csányi (Cambridge), Livia B. Pártay (Cambridge),
and Robert Baldock (Cambridge) for valuable conversations.
